---
title: "Sales Analysis"
author: "Cristian"
date: "9/8/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the Packages, data, and make the necessary changes to the columns 

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
#read the data
byte_fridges         = read_csv("Byte_Fridges.csv")
#assign a data type 
byte_fridges$Product = as.factor(byte_fridges$Product)
#adjust date format 
byte_fridges$Date    = as.Date(byte_fridges$Date,"%m/%d/%y")
#see the data 
glimpse(byte_fridges)
#view the list of products
AM_products          = unique(byte_fridges$Product)
print(AM_products)
```

Here we select the SLS-Products we want to look into 

```{r}
#List of the SLS products of interest 
SLS_Products        = c("Dark Chocolate PB Cups","DrinkSimple Maple Water", "Atomic Coffee - Cold Brew", "Bottle Water",
                         "Coconut Water", "Kind Bars", "Kombucha", "Krave Beef Jerky", "Love Corn", 
                         "Sparkling Raspberry Maple Water", "Trail Mix Pack Cranberry", "Tru Energy", "Wonderful Pistachios",
                         "SmartSweets Gummy Bears", "Sparkling Water", "Lifeway Kefir", "6AM Health Juice - Cleanse", 
                         "6AM Health Juice - Immune", "Dirty Lemon Water")
#Filter by the target products 
byte_fridges        = filter(byte_fridges, Product %in% SLS_Products)
#see the data 
glimpse(byte_fridges)
```
First we subset by date then we look at the 
Take a look at the table with SLS products sorted from largest units sales to the lowest 
```{r, echo=FALSE}
#subset the first week 
June_Week1                  = byte_fridges                            %>%
                              subset(Date> "2019-06-08" & Date < "2019-06-14") 
#group by store name and product 
June_Week1_location_sales = June_Week1                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(June_Week1_location_sales))
cat("\n")
#group by store name and product  
June_Week1_Summary        = June_Week1                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(June_Week1_Summary))
cat("\n")
June_Week1_plot           = ggplot(June_Week1 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "June 6th - June 14th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
June_Week1_plot
```

```{r, echo=FALSE}
June_Week2                = byte_fridges                                 %>%
                              subset(Date> "2019-06-15" & Date < "2019-06-21") 
#group by store name and product 
June_Week2_location_sales = June_Week2                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(June_Week2_location_sales))
cat("\n")
#group by store name and product  
June_Week2_Summary        = June_Week2                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(June_Week2_Summary))
cat("\n")
June_Week2_plot           = ggplot(June_Week2 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "June 15th - June 21st: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
June_Week2_plot
```

```{r,echo=FALSE}
June_Week3                = byte_fridges                               %>%
                              subset(Date> "2019-06-22" & Date < "2019-06-28") 
#group by store name and product 
June_Week3_location_sales = June_Week3                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(June_Week3_location_sales))
cat("\n")
#group by store name and product  
June_Week3_Summary        = June_Week3                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(June_Week3_Summary))
cat("\n")
June_Week3_plot           = ggplot(June_Week3 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "June 22nd - June 28th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
June_Week3_plot
```

```{r,echo=FALSE}
July_Week4                = byte_fridges                              %>%
                              subset(Date> "2019-06-29" & Date < "2019-07-05") 
#group by store name and product 
July_Week4_location_sales = July_Week4                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(July_Week4_location_sales))
cat("\n")
#group by store name and product  
July_Week4_Summary        = July_Week4                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(July_Week4_Summary))
cat("\n")
July_Week4_plot           = ggplot(July_Week4 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "June 28th - July 5th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
July_Week4_plot
```

```{r}
July_Week5                = byte_fridges                              %>%
                              subset(Date> "2019-07-06" & Date < "2019-07-12") 
#group by store name and product 
July_Week5_location_sales = July_Week5                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(July_Week5_location_sales))
cat("\n")
#group by store name and product  
July_Week5_Summary        = July_Week5                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(July_Week5_Summary))
cat("\n")
July_Week5_plot           = ggplot(July_Week5 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "July 6th - July 12th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
July_Week5_plot
```

```{r}
July_Week6                = byte_fridges                               %>%
                              subset(Date> "2019-07-13" & Date < "2019-07-19") 
#group by store name and product 
July_Week6_location_sales = July_Week6                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(July_Week6_location_sales))
cat("\n")
#group by store name and product  
July_Week6_Summary        = July_Week6                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(July_Week6_Summary))
cat("\n")
July_Week6_plot           = ggplot(July_Week6 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "July 13th - July 19th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
July_Week6_plot
```

```{r}
July_Week7                = byte_fridges                              %>%
                              subset(Date> "2019-07-20" & Date < "2019-07-26") 
#group by store name and product 
July_Week7_location_sales = July_Week7                                   %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(July_Week7_location_sales))
cat("\n")
#group by store name and product  
July_Week7_Summary        = July_Week7                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(July_Week7_Summary))
cat("\n")
July_Week7_plot           = ggplot(July_Week7 )                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "July 20th - July 26th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
July_Week7_plot
```
```{r}
July_ALL                = byte_fridges                                %>%
                              subset(Date> "2019-07-01" & Date < "2019-07-31") 
#group by store name and product 
July_ALL_location_sales = July_ALL                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(`Store Name`))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(July_ALL_location_sales))
cat("\n")
#group by store name and product  
July_ALL_Summary        = July_ALL                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(July_ALL_Summary))
cat("\n")
July_ALL_plot           = ggplot(July_ALL)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "July 1st - July 31st: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
July_ALL_plot
```

```{r}
August_Week8                = byte_fridges                            %>%
                              subset(Date> "2019-07-27" & Date < "2019-08-03") 
#group by store name and product 
August_Week8_location_sales = August_Week8                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week8_location_sales))
cat("\n")
#group by store name and product  
August_Week8_Summary        = August_Week8                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week8_Summary))
cat("\n")
August_Week8_plot           = ggplot(August_Week8)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "July 27th - August 3nd: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week8_plot
```

```{r}
August_Week9                = byte_fridges                            %>%
                              subset(Date> "2019-08-04" & Date < "2019-08-10") 
##group by store name and product 
August_Week9_location_sales = August_Week9                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week9_location_sales))
cat("\n")
#group by store name and product  
August_Week9_Summary        = August_Week9                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week9_Summary))
cat("\n")
August_Week9_plot           = ggplot(August_Week9)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "August 4th - August 10th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week9_plot
```

```{r}
August_Week10                = byte_fridges                           %>%
                              subset(Date> "2019-08-11" & Date < "2019-08-17") 
##group by store name and product 
August_Week10_location_sales = August_Week10                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week10_location_sales))
cat("\n")
#group by store name and product  
August_Week10_Summary        = August_Week10                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week10_Summary))
cat("\n")
August_Week10_plot           = ggplot(August_Week10)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "August 11th - August 17th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week10_plot
```

```{r}
August_Week11                = byte_fridges                           %>%
                              subset(Date> "2019-08-18" & Date < "2019-08-24") 
##group by store name and product 
August_Week11_location_sales = August_Week11                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week11_location_sales))
cat("\n")
#group by store name and product  
August_Week11_Summary        = August_Week11                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week11_Summary))
cat("\n")
August_Week11_plot           = ggplot(August_Week11)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "August 18th - August 24th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week11_plot
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
August_Week12                = byte_fridges                           %>%
                              subset(Date> "2019-08-25" & Date < "2019-08-31") 
##group by store name and product 
August_Week12_location_sales = August_Week12                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week12_location_sales))
cat("\n")
#group by store name and product  
August_Week12_Summary        = August_Week12                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week12_Summary))
cat("\n")
August_Week12_plot           = ggplot(August_Week12)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "August 25th - August 31st: Sales for SLS Stable Products")+
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week12_plot
```

```{r}
August_Week13                = byte_fridges                           %>%
                              subset(Date> "2019-09-01" & Date < "2019-09-07") 
##group by store name and product 
August_Week13_location_sales = August_Week13                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_Week13_location_sales))
cat("\n")
#group by store name and product  
August_Week13_Summary        = August_Week13                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_Week13_Summary))
cat("\n")
August_Week13_plot           = ggplot(August_Week13)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "September 1st - September 7th: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_Week13_plot
```

```{r}
August_ALL                = byte_fridges                              %>%
                              subset(Date> "2019-08-01" & Date < "2019-08-31") 
##group by store name and product 
August_ALL_location_sales = August_ALL                                  %>%
                            group_by(`Store Name`, Product)              %>%
                            summarise(Total_Unit_Sales    = sum(Qty))    %>%
                            arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product sales by location')
print(as.data.frame(August_ALL_location_sales))
cat("\n")
#group by store name and product  
August_ALL_Summary        = August_ALL                                   %>% 
                              group_by(Product)                          %>% 
                              summarise(TotaL_Sales = sum(Total),
                                        Total_Unit_Sales = sum(Qty))     %>% 
                              arrange(desc(Total_Unit_Sales))
print('This is the breakdown of SLS Product and Aggregate sales')
print(as.data.frame(August_ALL_Summary))
cat("\n")
August_ALL_plot           = ggplot(August_ALL)                                                                            +
                              geom_bar(aes(x = Date, y = Qty, color = Product), alpha = 0.6, size = 0.6, stat= "identity")     +
                              labs(x= "Date", y = "Total Units Sold", title = "August 1st - August 31st: Sales for SLS Stable Products")             +
                              scale_x_date(breaks = date_breaks("1 day"), labels = date_format("%m-%d"))                      +
                              scale_y_continuous(breaks = seq(1, 100, 1))  +
                              theme(axis.text.x = element_text(angle = 60, hjust = 1))
August_ALL_plot
```

